Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems

### 2019-04-06 ApproximateCode.tex
Version 2

\begin{abstract}
Erasure codes are commonly used to ensure data availability in cloud storage systems, where video data produced by autopilot, multimedia industry and security monitoring occupies large amounts of space.
Typical erasure codes, such as Reed-Solomon (RS) \cite{macwilliams1977theory} codes or XOR-based codes use several parity disks to equally back up all data.
However, this is expensive, not only because simultaneous damage of multiple disks is relatively rare, but also due to the ignorance of redundant information inside the data, which results in multiple complete parity disks being excessive.

Therefore, we propose Approximate Codes for video data, which significantly reduce storage overhead and increase availability for more important data segments.
Approximate Codes provide complete recovery when fewer disks fail, and ensure approximate recovery (recover most data) in the event of multiple disk failures.
To demonstrate the effectiveness of Approximate Codes, we conduct several experiments in Hadoop and Alibaba Cloud systems.
The results show that compared with the typical high-reliability erasure code schemes, Approximate Codes reduce the storage overhead by 7.64\% at the expense of reasonable probability of video quality loss.
\end{abstract}

>>>>

\begin{abstract}
Multimedia data generated by autonomous driving, media industry and security monitoring is often stored in cloud storage systems and occupies a large amount of space. Meanwhile, to ensure the data reliability, distributed file systems usually use erasure code redundant data. However, the commonly used triple disk failure tolerant arrays (3DFTS) erasure code scheme is expensive not only because simultaneous damage of multiple disks is relatively rare, but also due to its ignorance of redundant information inside the data, resulting in multiple complete parity disks being excessive. On the other hand, the recently proposed approximate storage scheme can effectively reduce storage costs, but at the cost of sacrificing the reliability of some data.

In this article, we propose Approximate Code for multimedia applications, which is an erasure code using an approximation strategy. Approximate Code aims to ensure different reliability of important and minor data by means of erasure coding, thereby reducing storage overhead. It provides complete recovery when fewer disks fail, and ensures approximate recovery (recover most data) in the event of multiple disk failures. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop and Alibaba Cloud systems. The results show that compared with the typical high-reliability erasure code schemes, Approximate Code reduces the storage overhead by 7.64\% at the expense of reasonable probability of data quality loss.

\end{abstract}
